Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-22 MS_thesis.tex
Fix how fancyhdr looks in the bibliography section
Aesthetic changes to in-text citations and bibliography
Adjust spacing between bib entries
Add acknowledgements

@@

\dedication{This thesis is dedicated to ?}

@@

%The acknowledgements go here. IISER guidelines say it should be <= 250 words.
\acknowledgments{
Not more than 250 words
}
\allowdisplaybreaks %allow align envts to go across pages

@@

\begin{document}

\pagestyle{plain} %Don't make the initial frontmatter fancy

@@

@@

%Import the Appendices
\chapter{From It\^{o} to Fokker-Planck}\label{App_SDE_FPE}
\input{ind_files/99_Appendix_A}
\chapter{Deriving stochastic trait frequency dynamics using It\^{o}'s formula}\label{App_density_to_freq}
\input{ind_files/99_Appendix_B}
\chapter{A Price-like equation for the variance of a type-level quantity}\label{App_stoch_var_eqns}
\input{ind_files/99_Appendix_C}
\chapter{Some Examples}\label{App_examples}
\input{ind_files/99_Appendix_D_examples}ne

%Bibliography
%Again, add the phantomsection so that hyperref knows where to go
\cleardoublepage
\phantomsection
\Huge\printbibheading
%Putting \printbibheading up here makes sure the heading is printed before I change the font size below.
%Change the font for the bibliography
\renewcommand*{\bibfont}{\footnotesize}	
%Add the bibliography
\printbibliography[heading=none]
%Add an entry in the table of contents
\addcontentsline{toc}{part}{References}

%And we're done :)
\end{document}

>>>>

\usepackage[final]{microtype} % microtype makes `subliminal improvements' in typesetting.
%see http://www.khirevich.com/latex/microtype/

@@

%Dedication
\dedication{This thesis is dedicated to ?}

@@

%The acknowledgements go here.
\acknowledgments{
%\vspace{-0.5cm}
First and foremost, I am grateful to my advisors, Prof. Vishwesha Guttal and Prof. Rohini Balakrishnan, for their masterful mentoring. The enormous academic freedom they gave me to pursue essentially whichever ideas seemed promising at the time, coupled with their readiness to provide detailed guidance whenever I asked for it, made working with them an incredibly enriching experience. Their constant focus on the bigger picture was vital to helping me see the forest when I was stuck looking at the trees. Both Vishu and Rohini are brilliant scientists and fantastic mentors, and their mentorship and guidance have deeply impacted my ways of thinking about science and mentoring. I am also grateful to all the members of the \href{https://teelabiisc.wordpress.com/}{Theoretical Ecology and Evolution lab} and the \href{https://sites.google.com/view/rohinibalakrishnanlab/home}{Animal Communication and Bioacoustics Lab} for providing a supportive and productive working environment.

I would also like to thank Prof. Sutirth Dey, my expert for this project. Sutirth provided constructive comments during the mid-year evaluation that helped me re-evaluate my project and its goals. Sutirth's brilliant course on evolution at IISER and various fascinating conversations with him and other lab members during my time as an intern at the \href{https://sites.google.com/a/acads.iiserpune.ac.in/sdlab/pbl-iiser-p}{Population Biology Lab} have been instrumental in shaping my thoughts on evolution.

I am grateful to many friends who made the IISER journey enjoyable. Countless long days and nights with Adithyan, Abhishek, Arjun, Chebi, Gaurav, Harshit, Manas, Milie, and Shruthi, have greatly helped me grow as a person, both intellectually and emotionally. I love all of y'all. Arjun has always been a great sounding board for my thoughts, no matter how inane, and has been very patient and supportive in more ways than I could list here. Milie is the occasional fitness friend that everyone needs, and occasionally texting her encouraged me to hit the gym at least semi-regularly even during hectic parts of the thesis project when schedules were uncertain. I am indebted to our D\&D group in general and Manas in particular for introducing me to D\&D and Critical Role, both of which were very helpful in getting through the pandemic as well as the thesis. Shruthi is a constant source of cat related mental health boosts and has more generally taught me a lot about a lot during my time at IISER. I am also grateful to Abhishek for letting me bother him with various physics-related questions throughout the project year. I entered this project as someone who knew some mathematics and some biology but quickly realized I would benefit from reading physics papers (typically written in physics language). Abhishek patiently answered all my basic questions about physics language/tools and skillfully helped me understand how physicists think. Insightful conversations about evolution with Gaurav were formative in gaining fresh perspectives on various topics. Closer to home, Akshay and Prerana have been my closest friends since high school and continue to provide unerring and unconditional love and support. I don't know where I would be without them today.

I am also grateful to various non-human companions, canine, feline, and more exotic. The dogs and cats of ISI are more helpful to my mental health than I could possibly articulate. Even though my thesis work may seem dreadfully abstract, running after pretty animals in the Western Ghats and other wild places of India is how I even got interested in science in the first place, and I certainly wouldn't be here today if the animals weren't so fascinating :)

%I would like to thank the KVPY fellowship program (now the INSPIRE program) by the Department of Science and Technology, Government of India, for providing me with financial support for the duration of my time at IISER. I would also like to thank the PARAM-Brahma facility at IISER Pune, part of the National Supercomputing Mission, Government of India, for providing me with computing resources, though I did not finally end up using the facility for this thesis.

Finally, I am eternally indebted to my parents, Raja and Vidya. They have quite literally supported me at every step of my life, and have nurtured and encouraged an inquisitive wonder of the world that no doubt played a vital role in helping me choose this career path. Not many parents would raise their children on Durrell and Feynman or take time out of their day to help their child find the right plant or jar for keeping an insect in the house. Upon finding out that their child has an early fascination with praying mantids and finding that there is no accessible information about the topic, not many parents would encourage their child to try and write their own source on the subject by keeping these insects at home and documenting their behavior. Upon finding out that their child was interested in snakes, not many parents would encourage this interest and actively accompany them to animal rescue centers, snake parks, and herpetology summer camps. Not many parents would be okay with their child spending weeks in the rainforest  with virtual strangers and no cellular network, catching snakes and looking for frogs in the dark with a flashlight. Certainly, not many Indian parents would let their child pursue this love of animals professionally and allow them to virtually ignore the more `mainstream' entrance exams for engineering and medical colleges in favor of pursuing the relative pipe dream of getting a KVPY scholarship for admission to an IISER or IISc. Not many parents would provide an actively supporting environment at home for an MS project, without questioning their child's future plans or PhD application process at any stage, and just trusting that the child will figure things out. Not many parents would provide fantastic support during difficult emotional situations or not blink an eye when their child decides to grow their hair out or get a tattoo (or two). Thank you for always believing in me and for letting me pursue my passions; I would be nothing without you. 
}
\allowdisplaybreaks %allow align envts to go across pages

@@

\begin{document}
\microtypesetup{disable}
\pagestyle{plain} %Don't make the initial frontmatter fancy

@@

%Enable microtype from here on out
\microtypesetup{enable}

@@

%Import the Appendices
\chapter{From It\^{o} to Fokker-Planck}\label{App_SDE_FPE}
\input{ind_files/99_Appendix_A}
\chapter{Deriving stochastic trait frequency dynamics using It\^{o}'s formula}\label{App_density_to_freq}
\input{ind_files/99_Appendix_B}
\chapter{A Price-like equation for the variance of a type-level quantity}\label{App_stoch_var_eqns}
\input{ind_files/99_Appendix_C}
\chapter{Some Examples}\label{App_examples}
\input{ind_files/99_Appendix_D_examples}

%Bibliography

%You dont need the `Appendix X' prefix in the headers of the bibliography. 
\fancyhead[CO]{\rule[-4ex]{0pt}{4ex}\footnotesize\itshape\nouppercase{\leftmark}}
%Add the phantomsection so that hyperref knows where to go
\cleardoublepage
\phantomsection
\Huge\printbibheading
%Add an entry in the table of contents
\addcontentsline{toc}{part}{References}
%Putting \printbibheading up here makes sure the heading is printed before I change the font size below. This should also be outside of multicol if you use a multi-column bibliography.
%Change the font for the bibliography
\renewcommand*{\bibfont}{\footnotesize}	
%Typeset the bibliography little differently using ragged2e
\begingroup
\RaggedRight
%Add the bibliography
\printbibliography[heading=none]
\endgroup
%And we're done :)
\end{document}
